Self Regulation Ontology Retest Analyses

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem plots

```{r}
tmp = duplicate_items_data_t1 %>%
  gather(key, value, -worker)

@@

tmp = duplicate_items %>%
  select(item1_ID, item2_ID) %>%
  left_join(tmp, by = c("item1_ID" = "key")) %>%
  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
  group_by(item1_ID) %>%
  mutate(item1_time1 = scale(item1_time1),
         item1_time2 = scale(item1_time2),
         item2_time1 = scale(item2_time1),
         item2_time2 = scale(item2_time2)) %>%
  ungroup()

@@

ggplotly(p1)

grid.arrange(p1, p2, p3, p4, ncol=2)

rm(tmp, tmp2)
```

@@

```{r}
summary(rel_comp$sample_size[rel_comp$task == "survey"])
summary(rel_comp$sample_size[rel_comp$task == "task"])
```

@@

```{r}
rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  geom_point(alpha = 0.2)+
  theme(legend.title = element_blank())+
  xlab("Sample Size")+
  ylab("Retest reliability")
```

@@

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n())
```

>>>>

```{r warning=FALSE, message=FALSE}
tmp = duplicate_items_data_t1 %>%
  gather(key, value, -worker)

@@

tmp = duplicate_items %>%
  select(item1_ID, item2_ID) %>%
  left_join(tmp, by = c("item1_ID" = "key")) %>%
  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
  group_by(item1_ID) %>%
  mutate(item1_time1 = scale(item1_time1),
         item1_time2 = scale(item1_time2),
         item2_time1 = scale(item2_time1),
         item2_time2 = scale(item2_time2),
         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
  ungroup()

@@

p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)

ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)

rm(tmp, tmp2, p1, p2, p3, p4, p5)
```

@@

```{r}
summary(rel_comp$sample_size[rel_comp$task == "survey"])
summary(rel_comp$sample_size[rel_comp$task == "task"])

rel_comp %>%
  group_by(task) %>%
  summarise(mean_sample_size = mean(sample_size),
            sem_sample_size = sem(sample_size)) %>%
  ggplot(aes(task,mean_sample_size,col=task))+
  geom_point(size=5)+
  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
  xlab("")+
  ylab("Sample size")+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))

ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  geom_point(alpha = 0.2)+
  theme(legend.title = element_blank())+
  xlab("Sample Size")+
  ylab("Retest reliability")

ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n()) %>%
  mutate(total_num_vars = c(74, 372),
         prop = count/total_num_vars) %>%
  ggplot(aes(task, prop, fill=task))+
  geom_bar(stat="identity", alpha=0.5, width=0.5)+
  theme(legend.position = "none", 
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  ylab("Proportiono of samples")+
  xlab("")

ggsave('PropTimeEffects.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
